The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-18 paper2_JNLS/paper.tex
NM

\section{Introduction}

%----------------------------------------------------------%
% Mathematical framework
%----------------------------------------------------------%
\section{The truncated KdV framework}

>>>>

%----------------------------------------------------------%
% Intro
%----------------------------------------------------------%
\section{Introduction}

Introduce waves. \\
Introduce papers: PRF, PNAS, and J Stat Phys. \\

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in PNAS for the sake of brevity.
\item Provide additional experimental measurements not presented in Bolles PRF. For example, statistics on surface slope and autocorrelation.
\end{itemize}

%----------------------------------------------------------%
% Experiments
%----------------------------------------------------------%
\section{The experiments}

%----------------------------------------------------------%
% Theory
%----------------------------------------------------------%
\section{The truncated KdV framework}
